\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}. Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems. A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.

\medskip
In oil and gas reservoir exploration, viscous and density fingers are relatively common in reservoirs with water-injection wells. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}. The result of fingering is an inefficient sweeping efficiency that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores. This instability is mainly governed by the ratio of mobility (MR) of the displacing and the displaced fluids (mobility-ratio, MR). %In a water-oil system the MR is given by eq.\ref{eq:MR}.

\medskip
In large scale field O$\&$G operations, viscous or density fingering is a relatively common condition in reservoirs with water-injection wells. As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}. The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores. This instability is mainly governed by the ratio of mobility (MR) of the displacing fluid and the of the displaced fluid (mobility-ratio, MR). %In a water-oil system the MR is given by eq.\ref{eq:MR}.
However, other important factors that also influence the severity of viscous fingering are: heterogeneous permeability fields, gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.

@@

%\begin{figure}[h]
%\centering
%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored)blue points represent the pressure nodes and white points the velocity nodes.}
%\label{fig:fem_cv}
%\end{figure}

%\begin{figure}[h]
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Figs/p1dgp2-cont-sat.pdf}
%             \includegraphics[width=.5\textwidth]{./Figs/p2dgp1-dg-sat.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{5.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
\label{fig:fem_cv}
\end{figure}

@@

%\begin{figure}[h] 
%\centering
%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
%\caption{This is a description of two different element types. Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$. Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$. The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise. }
%\label{fig:fem_elem}
%\end{figure}

\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
\caption{This is a description of two different element types. Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$. Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$. The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise. }
\label{fig:fem_elem}
\end{figure}

@@

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\centering
%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
%\caption{Caption 3}
%\label{fig:subim3}
%\end{center}

%\caption{Caption for this figure with two images}
%\label{fig:image1}
%\end{figure}
%\pagebreak
%\clearpage

\pagebreak
\clearpage
%\input{article_figure1}
%\input{Manuscript_Figure1}

@@

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
%\label{fig:simple_case}
%\end{center}
%\end{figure}

\begin{figure}[h]
\centering
\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
\label{fig:simple_case}
\end{figure}

@@

%\begin{figure}[h]
%\begin{center}
%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region. The mesh is unstructured and fixed with 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
%\label{fig:square}
%\end{center}
%\end{figure}

%\begin{figure}[h]
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a)  
}
\vspace{0.5cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
}
\vspace{1.0cm}
\hbox{\hspace{5.0cm} (b)  
}}     
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fem_cv_represent_a}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end   
}
}     
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%%%%%%%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=2000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000     
}
}     
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=24000     
}
}     
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}

%{./Pics/P1DG-P2_element_type} 
%{./Pics/4r_po_adapt_fine_125_mesh} 
%{./Pics/4r_po_adapt_fine_100_mesh}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b)      
}
}     
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=250   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
\label{fig:2testcase_b}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

%%%%%%%%%%%%%
\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}

@@

%\begin{figure}[h]
%\vbox{
%\hbox{\hspace{3.5cm}
%\includegraphics[width=.5\textwidth]{} 
%}
%\vspace{0.0cm}
%\hbox{\hspace{5.0cm} (a)    
%}
%\vspace{0.25cm}
%\hbox{\hspace{3.5cm}
%\includegraphics[width=.5\textwidth]{}
%}
%\vspace{0.0cm}
%\hbox{\hspace{5.0cm} (b)      
%}
%}     
%\caption{}
%\label{}
%\end{figure}

%%%%
%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
%%%%

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

%\begin{figure}[h]
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}\\[0.5cm]% If you want some vertical space
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}%
%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
%\label{fig:3testcase_b}
%\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_c}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_d}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
}
}     
\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
}
}     
\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
\label{fig:4testcase_b}
\end{figure}

@@

\clearpage
\listoffigures

@@

>>>>

Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}. Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems. A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}. 
In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes. As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}). Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells. Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids. Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.

@@

@@

@@

@@

@@

@@

@@

@@

@@

\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}

@@

@@

@@

@@

\clearpage
\listoffigures
\clearpage

\input{article_figure1}
%\input{article_figure2}
